Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-04 programlogic.tex
+

  \item Page Map Level-4 Translation (L4): Calculating the offset to the 4 \textsf{Kbyte Physical Page} table to obtain the  physical address by  which resides in the last 12 bits of the virtual memory address, $\locsf|^{12}$,  shown in Figure \ref{}.
    % \pfpointsto{\lvlsum\crt\lfoff}{\lvlbor\lt}\qfracfotsss\ppts \ast

@@

  \item Page Directory Pointer Level Translation (L3):

@@

  \item Page Directory Table Level Translation (L2):  we obtain the address of the page table via \textsf{PDE}$|^{52}$ and picking the offset from the virtual memory address via imposing the mask to obtain page table offset bits (9 bits [20-12] shown in Figure \ref{}) to obtain the page table entry (\textsf{PTE}).

>>>>

  \item Page Map Level-4 Translation (L4): Address translation, handling the first level (to get the PML4E entry) itself by calculating the offset (\textsf{CR3}$|^{12}$) and frame (PML4E$|^{52}$) via masking with the root address space address currently stored in \textsf{CR3}.

@@

  \item Page Directory Pointer Level Translation (L3): Performs the second level of address translation via interpreting, in other words masking, the PML4 entry (PML4E$|^{52}$) to retrieve the starting address of a page-directory-pointer-table and the offset ( (PML4E$|^{9}$)) to the entry

@@

  \item Page Directory Table Level Translation (L2):  Performs the third level of address translation by retrieving the starting address at the PD table (PDPE$|^{52}$), and interprets a PDPE ($|^{9}$) that references the PD table entry.
